Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-03-23 ms.qmd
Added bold format

# Create the table
  tabs1 <- rbind(fixed, random)
  gt(tabs1) %>%  fmt_number(
    columns = 2:5,
    decimals = 2
  ) %>% tab_row_group(label = "Fixed Effects", rows = 1:7) %>% tab_row_group(label = "Random Effects", rows = 8:11)
```

>>>>

# Create the table
  tabs1 <- rbind(fixed, random)
  gt(tabs1) %>%  
  fmt_number(columns = 2:5, decimals = 2) %>% 
  tab_row_group(label = "Fixed Effects", rows = 1:7) %>% 
  tab_row_group(label = "Random Effects", rows = 8:11) %>%  
  tab_style(style = list(cell_text(weight = "bold")),
        locations = list(cells_column_labels(), cells_row_groups()))
```
